%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvtheme[grey]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}

%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Andrew}
\familyname{Bacon}
\address{Department of Philosophy, University of Southern California}{3709 Trousdale Parkway, Los Angeles, CA 90089}    % optional, remove the line if not wanted
\mobile{1 323 600 5498}                    % optional, remove the line if not wanted
%\phone{1 213 821 4116}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{abacon@usc.edu}                      % optional, remove the line if not wanted
\extrainfo{https://andrew-bacon.github.io/} % optional, remove the line if not wanted

%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Employment}
\cventry{2018--present}{Associate Professor}{}{University of Southern California}{}{}  % arguments 3 to 6 are optional
\cventry{2013--2018}{Assistant Professor}{}{University of Southern California}{}{}  % arguments 3 to 6 are optional
\cventry{2010--2012}{Prize Fellow by Examination}{Magdalen College}{Oxford University}{}{}  % arguments 3 to 6 are optional

\section{Education}
\cventry{2009--2012}{DPhil}{Oxford University}{Supervised under Cian Dorr (primary) and Timothy Williamson}{}{Indeterminacy: An Investigation Into The Soritical And Semantical Paradoxes}  % arguments 3 to 6 are optional
\cventry{2007--2009}{BPhil}{Oxford University}{}{\textit{Distinction}}{Philosophy}  % arguments 3 to 6 are optional
\cventry{2003--2007}{MMathPhil}{Oxford University}{}{\textit{First class}}{Maths and Philosophy}  % arguments 3 to 6 are optional

\section{Areas of specialisation}
\cvlistitem{Philosophy of Language, Philosophical Logic, Metaphysics, Epistemology.}

%\section{Areas of competence}
%\cvlistitem{Philosophy of Physics, Epistemology, Philosophy of Mathematics, Frege, Mathematical Logic}



\section{Prizes and honours}

\cvlistitem{Awarded the 2016 Sanders Prize in Metaphysics for the article `Relative Locations'. \$10,000 awarded annually to a scholar no more than 15 years from their PhD.}
\cvlistitem{Article `Stalnaker's Thesis in Context' selected for the Philosopher's Annual 2015 (selection of the ten best articles each year).}
\cvlistitem{Article `Quantificational Logic and Empty Names' selected for the Philosopher's Annual 2013 (selection of the ten best articles each year).}
\cvlistitem{American Philosophical Association Article Prize (for the article `Quantificational Logic and Empty Names'). \$2000 awarded best article published between 2012 and 2013 by a scholar under 40 or within 10 years of recieving their PhD.}
\cvlistitem{Prize Fellow by Examination, Magdalen College. 2010.}
\cvlistitem{Gilbert Ryle Prize for best overall performance in BPhil examinations, 2009. \pounds 500.}
\cvlistitem{John Locke Prize in Mental Philosophy, 2008. \pounds 500 awarded by six hour exam.}
\cvlistitem{Wykeham Scholarship at New College, Oxford University. 2007-2011}
\cvlistitem{AHRC Scholarship. 2007-2011}
\cvlistitem{Gibbs Prize in Philosophy, awarded for outstanding performance in the Philosophy papers in each of the joint Honour Schools involving Philosophy. Oxford University 2007.}
\cvlistitem{Scholarship at Lady Margaret Hall, Oxford University. 2004-2007.}

%\newpage





\section{Publications and books}

\cvlistitem{\emph{Vagueness and Thought}. Book with Oxford University Press (May 2018).}
\cvlistitem{Logical Combinatorialism. \emph{Philosophical Review}. Forthcoming}
\cvlistitem{Opacity and Paradox. For \emph{Modes of Truth: The unified approach to truth, modality, and paradox}. Carlo Nicolai and Johannes Stern (eds).}
\cvlistitem{Counterfactuals, Infinity and Paradox. For \emph{Outstanding Contributions to Logic: Kit Fine}. Federico Faroldi and Frederik Van de Putte (eds).}
\cvlistitem{Substitution Structures. \emph{Journal of Philosophical Logic}. Forthcoming.}
\cvlistitem{Inductive Knowledge. \emph{Nous}. Forthcoming.}
\cvlistitem{Some results on the limits of thought. (with Gabriel Uzquiano). \emph{Journal of Philosophical Logic}, 47(6), 991-999.}
\cvlistitem{Is Reality Fundamentally Qualitative?. \emph{Philosophical Studies}. Forthcoming.}
\cvlistitem{The Logic of Opacity. (with Jeff Russell). \emph{Philosophical and Phenomenological Research}. Forthcoming.}
\cvlistitem{The Broadest Necessity. \emph{Journal of Philosophical Logic}. Volume 47, issue 5:733-783 2018.}
\cvlistitem{Radical Anti-Disquotationalism. \emph{Philosophical Perspectives}. Forthcoming.*}
\cvlistitem{Relative Locations. \emph{Oxford Studies in Metaphysics}. Volume 11, 2018.}
\cvlistitem{Tense and relativity. \emph{Nous}. Volume52, Issue 3. September 2018. Pages 667-696.}
\cvlistitem{Higher-Order Free Logic and the Prior-Kaplan Paradox. (with John Hawthorne and Gabriel Uzquiano). Williamson on Modality. Special volume of \emph{the Canadian Journal of Philosophy}, Routledge. 2017. Eds. Yli-Vakkuri, J. and McCullagh, M.*}
\cvlistitem{Scharp on Replacing Truth. \emph{Inquiry}. Volume 50, 2017 - Issue 6.*}
\cvlistitem{Can The Classical Logician Avoid The Revenge Paradoxes? \emph{Philosophical Review}. July 2015, Volume 124, Number 3: 299-352.}
\cvlistitem{Stalnaker's Thesis in Context. \emph{The Review of Symbolic Logic}. March 2015, Volume 8, Number 1, pp131-163. }
\cvlistitem{Paradoxes of Logical Equivalence and Identity. \emph{Topoi}. April 2015, Volume 34, Issue 1, pp 89-98.**}
\cvlistitem{Giving Your Knowledge Half a Chance.  \emph{Philosophical Studies}. November 2014, Volume 171, Issue 2, pp 373-397. }
\cvlistitem{Representing Counterparts. \emph{The Australasian Journal of Logic}. Vol 11, Number 2, November 2014.}
\cvlistitem{Quantificational Logic and Empty Names. \emph{Philosophers' Imprint}. Volume 13, Number 24, December 2013. }
\cvlistitem{A New Conditional for Na\"{i}ve Truth Theory. \emph{Notre Dame Journal of Formal Logic}. Volume 54, Number 1 (2013), 87-104. }
\cvlistitem{Curry's Paradox and Omega-inconsistency. \emph{Studia Logica}. Volume 101, Issue 1, February 2013, pp 1-9. }
\cvlistitem{Non-classical Metatheory for Non-classical Logics. \emph{Journal of Philosophical Logic}. April 2013, Volume 42, Issue 2, pp 335-355. }
\cvlistitem{Non-wellfounded Mereology. (with Aaron J. Cotnoir) \emph{The Review of Symbolic Logic}. Volume 5, Issue 02, June 2012, pp 187-204. }
\cvlistitem{A Paradox for Supertask Decision Makers. \emph{Philosophical Studies}: Volume 153, Issue 2 (2011), Page 307.}





%\newpage 
%\section{Languages}
%\cvlanguage{language 1}{Skill level}{Comment}
%\cvlanguage{language 2}{Skill level}{Comment}
%\cvlanguage{language 3}{Skill level}{Comment}

%\section{Computer skills}
%\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvcomputer{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvcomputer{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

%\section{Interests}
%\cvline{hobby 1}{\small Description}
%\cvline{hobby 2}{\small Description}
%\cvline{hobby 3}{\small Description}

\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.
