%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvtheme[grey]{classic} 
\usepackage[T1]{fontenc}
\usepackage{lmodern}


                % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}

%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Andrew}
\familyname{Bacon}
\address{Department of Philosophy, University of Southern California}{3709 Trousdale Parkway, Los Angeles, CA 90089}  

\email{abacon@usc.edu}                      % optional, remove the line if not wanted
\extrainfo{https://andrew-bacon.github.io/} % optional, remove the line if not wanted

%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
\quote{Last updated \today}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Employment}
\cventry{2023--present}{Full Professor}{}{University of Southern California}{}{}  % arguments 3 to 6 are optional
\cventry{2018--2023}{Associate Professor}{}{University of Southern California}{}{}  % arguments 3 to 6 are optional
\cventry{2013--2018}{Assistant Professor}{}{University of Southern California}{}{}  % arguments 3 to 6 are optional
\cventry{2010--2012}{Prize Fellow by Examination}{Magdalen College}{Oxford University}{}{}  % arguments 3 to 6 are optional

\section{Education}
\cventry{2009--2012}{DPhil}{Oxford University}{Supervised under Cian Dorr (primary) and Timothy Williamson}{}{Indeterminacy: An Investigation Into The Soritical And Semantical Paradoxes}  % arguments 3 to 6 are optional
\cventry{2007--2009}{BPhil}{Oxford University}{}{\textit{Distinction}}{Philosophy}  % arguments 3 to 6 are optional
\cventry{2003--2007}{MMathPhil}{Oxford University}{}{\textit{First class}}{Maths and Philosophy}  % arguments 3 to 6 are optional

\section{Areas of specialisation}
\cvlistitem{Philosophical Logic, Metaphysics, Language, Epistemology}




\section{Prizes and honours}

\cvlistitem{Awarded the 2016 Sanders Prize in Metaphysics for the article `Relative Locations'. \$10,000 awarded annually to a scholar no more than 15 years from their PhD.}
\cvlistitem{Article `Stalnaker's Thesis in Context' selected for the Philosopher's Annual 2015 (selection of the ten best articles each year).}
\cvlistitem{Article `Quantificational Logic and Empty Names' selected for the Philosopher's Annual 2013 (selection of the ten best articles each year).}
\cvlistitem{American Philosophical Association Article Prize (for the article `Quantificational Logic and Empty Names'). \$2000 awarded best article published between 2012 and 2013 by a scholar under 40 or within 10 years of recieving their PhD.}
\cvlistitem{Prize Fellow by Examination, Magdalen College. 2010.}
\cvlistitem{Gilbert Ryle Prize for best overall performance in BPhil examinations, 2009. \pounds 500.}
\cvlistitem{John Locke Prize in Mental Philosophy, 2008. \pounds 500 awarded by six hour exam.}
\cvlistitem{Wykeham Scholarship at New College, Oxford University. 2007-2011}
%\cvlistitem{AHRC Scholarship. 2007-2011}
%\cvlistitem{Gibbs Prize in Philosophy, awarded for outstanding performance in the Philosophy papers in each of the joint Honour Schools involving Philosophy. Oxford University 2007.}
%\cvlistitem{Scholarship at Lady Margaret Hall, Oxford University. 2004-2007.}

%\newpage

\section{Books}

\cvlistitem{\emph{Vagueness and Thought}. Oxford University Press (May 2018).}
\cvlistitem{\emph{A Philosophical Introduction to Higher-order Logics}. Routledge (September 2023).}

\section{Publications}

\cvlistitem{Mathematical Modality: A higher-order investigation. \emph{Journal of Philosophical Logic}. Forthcoming}
\cvlistitem{A Theory of Structured Propositions. \emph{Philosophical Review}. Forthcoming}

\cvlistitem{A Case for Higher-Order Metaphysics. For \emph{Higher-order Metaphysics}. Eds. Peter Fritz and Nicholas Jones. Forthcoming}

\cvlistitem{Actual Value in Decision Theory. \emph{Analysis}. Forthcoming}
\cvlistitem{Classicism. (With Cian Dorr) For \emph{Higher-order Metaphysics}. Eds. Peter Fritz and Nicholas Jones.}
\cvlistitem{A Theory of Necessities. (with Jin Zeng.) \emph{Journal of Philosophical Logic}. volume 51, pp.151-199 (2022).}
\cvlistitem{The Logic of Logical Necessity. (with Kit Fine). \emph{Saul Kripke on Modal Logic} (eds. Romina Padro and Yale Weiss). Forthcoming.}
\cvlistitem{Against Disquotation. (with Jeremy Goodman). \emph{Australasian Journal of Philosophy}. 100:4, 711-726 (2022)}

\cvlistitem{Vagueness at Every Order. \emph{Proceedings of the Aristotelian Society}. Volume 120, Issue 2, July 2020, Pages 165-201.}
\cvlistitem{Logical Combinatorialism. \emph{Philosophical Review}. 129 (4): 537-589 (2022).}
\cvlistitem{Opacity and Paradox. In \emph{Modes of Truth: The unified approach to truth, modality, and paradox}. Carlo Nicolai and Johannes Stern (eds). Routledge (2021)** }
\cvlistitem{Counterfactuals, Infinity and Paradox. In \emph{Outstanding Contributions to Logic: Kit Fine}. Federico Faroldi and Frederik Van de Putte (eds).}
\cvlistitem{Substitution Structures. \emph{Journal of Philosophical Logic}. 48, pages 1017-1075 (2019).}
\cvlistitem{Inductive Knowledge. \emph{Nous}. 54 (2): 354-388 (2020).}
\cvlistitem{Some results on the limits of thought. (with Gabriel Uzquiano). \emph{Journal of Philosophical Logic}, 47(6), 991-999.}
\cvlistitem{Is Reality Fundamentally Qualitative?. \emph{Philosophical Studies}. 176 (1): 259-295. 2019.}
\cvlistitem{The Logic of Opacity. (with Jeff Russell). \emph{Philosophical and Phenomenological Research}. 99 (1):81-114 (2019).}
\cvlistitem{The Broadest Necessity. \emph{Journal of Philosophical Logic}. Volume 47, issue 5:733-783 2018.}
\cvlistitem{Radical Anti-Disquotationalism. \emph{Philosophical Perspectives}. Philosophical Perspectives. (2018).*}
\cvlistitem{Relative Locations. \emph{Oxford Studies in Metaphysics}. Volume 11, 2018.}
\cvlistitem{Tense and relativity. \emph{Nous}. Volume52, Issue 3. September 2018. Pages 667-696.}
\cvlistitem{Higher-Order Free Logic and the Prior-Kaplan Paradox. (with John Hawthorne and Gabriel Uzquiano). Williamson on Modality. Special volume of \emph{the Canadian Journal of Philosophy}, Routledge. 2017. Eds. Yli-Vakkuri, J. and McCullagh, M.*}
\cvlistitem{Scharp on Replacing Truth. \emph{Inquiry}. Volume 50, 2017 - Issue 6.*}
\cvlistitem{Can The Classical Logician Avoid The Revenge Paradoxes? \emph{Philosophical Review}. July 2015, Volume 124, Number 3: 299-352.}
\cvlistitem{Stalnaker's Thesis in Context. \emph{The Review of Symbolic Logic}. March 2015, Volume 8, Number 1, pp131-163. }
\cvlistitem{Paradoxes of Logical Equivalence and Identity. \emph{Topoi}. April 2015, Volume 34, Issue 1, pp 89-98.**}
\cvlistitem{Giving Your Knowledge Half a Chance.  \emph{Philosophical Studies}. November 2014, Volume 171, Issue 2, pp 373-397. }
\cvlistitem{Representing Counterparts. \emph{The Australasian Journal of Logic}. Vol 11, Number 2, November 2014.}
\cvlistitem{Quantificational Logic and Empty Names. \emph{Philosophers' Imprint}. Volume 13, Number 24, December 2013. }
\cvlistitem{A New Conditional for Na\"{i}ve Truth Theory. \emph{Notre Dame Journal of Formal Logic}. Volume 54, Number 1 (2013), 87-104. }
\cvlistitem{Curry's Paradox and Omega-inconsistency. \emph{Studia Logica}. Volume 101, Issue 1, February 2013, pp 1-9. }
\cvlistitem{Non-classical Metatheory for Non-classical Logics. \emph{Journal of Philosophical Logic}. April 2013, Volume 42, Issue 2, pp 335-355. }
\cvlistitem{Non-wellfounded Mereology. (with Aaron J. Cotnoir) \emph{The Review of Symbolic Logic}. Volume 5, Issue 02, June 2012, pp 187-204. }
\cvlistitem{A Paradox for Supertask Decision Makers. \emph{Philosophical Studies}: Volume 153, Issue 2 (2011), Page 307. \\ (Standard peer review, unless otherwise indicated. *=invited contribution. **=invited and refereed.)}




\section{Papers in Progress}


\cvlistitem{Could the truths of mathematics have been different?}
\cvlistitem{Zermelian Extensibility (Under review)}
\cvlistitem{Counterfactuals in Thought}
\cvlistitem{What is the Logic of Conditionals?}
\cvlistitem{The Logic of Logical Atomism (with Peter Fritz)}
\cvlistitem{The Algebra of Logical Atomism (with Peter Fritz)}

\section{Talks}

\cventry{2023}{Higher-order metaphysics workshop}{July}{Oxford}{Invited}{TBA}
\cventry{2023}{Philosophy of Mathematics Seminar, Oxford University}{June}{Oxford}{Invited}{Zermelian Extensibility}
\cventry{2023}{TimFest}{July}{Oxford}{Invited}{Classicism, Weak Classicism, and Necessitism (with Cian Dorr)}
\cventry{2023}{American Philosophical Association}{March}{San Francisco}{Invited}{Could possibility be indefinitely extensible?}

\cventry{2022}{University of Southern California}{June}{Los Angeles}{Invited}{Higher-order modal metaphysics and the continuum hypothesis}

\cventry{2022}{American Philosophical Association}{March}{Vancouver}{Invited}{Modal Logicism}
\cventry{2022}{American Philosophical Association}{March}{Vancouver}{Invited}{Commentator on Kit Fine's `Vagueness: A Global Approach'}
\cventry{2022}{University of Texas, Austin}{March}{Austin}{Invited}{A Theory of Structured Propositions}

\cventry{2021}{University of Bristol}{October}{Bristol (by zoom)}{Invited}{Counterfactuals in Thought}

\cventry{2021}{Munich Center for Mathematical Philosophy}{December}{Munich (by zoom)}{Invited}{Counterfactuals in Thought}




\cventry{2021}{American Philosophical Association, Pacific}{April}{By zoom}{Invited}{}
\cventry{2021}{American Philosophical Association, Estern}{January}{By zoom}{Invited}{Fundamentality: A Logical Framework}

\cventry{2020}{Princeton Talks on Epistemology and Metaphysics}{March}{Princeton University}{Invited}{Vagueness at Every Order}
\cventry{2020}{Aristotelian Society}{16th March}{}{Invited}{Vagueness at Every Order}

\cventry{2019}{University of Chapel Hill}{September}{}{Invited}{Commentary on Kit Fine's truthmaker semantics for counterfactuals}
\cventry{2019}{Kings College Masterclass}{May}{Kings College London}{Invited}{Masterclass on Higher-order Metaphysics}
\cventry{2018}{New York University}{November 16th}{New York}{Invited}{Radical Anti-Disquotationalism}
\cventry{2018}{Semantic Paradox and Revenge}{June 27th-29th}{Salzburg}{Invited}{Propositional granularity and the logical paradoxes}
\cventry{2018}{Mini-workshop on Vagueness and Modality}{June 25th}{Humboldt University}{Invited}{Logical Combinatorialism}
\cventry{2018}{Princeton Talks on Epistemology and Metaphysics}{April 21}{Princeton University}{Invited}{Inductive Knowlege}
\cventry{2017}{Symposium on Sarah Moss's `Probabilistic Knowledge'}{August 16th - 18th}{Hamburg}{Invited}{`Expressivist Approaches to Indicative Conditionals'}
\cventry{2017}{Jowette Society}{May 19th}{University of Oxford}{Invited}{`The Broadest Necessity'}
\cventry{2017}{Metaphysics on the Mountain}{March 13th-17th}{Sun Valley, Idaho}{Invited}{`Is Reality Fundamentally Qualitative?'}

\cventry{2016}{Workshop on Higher-Order Metaphysics}{June 5th}{Oslo}{Submitted}{`The Logic of Opacity' (with Jeff Russell)}
\cventry{2016}{Meaning Sciences Club}{March 12-13}{UC Berkeley}{Invited}{On the Semantics of Indicatives}
\cventry{2015}{Williamson in Montreal}{April 22nd-25th}{A workshop for the contributors to Williamson on Modality}{Invited}{`Higher Order Free Logic and the Prior-Kaplan Paradox'}
\cventry{2015}{Symposium on Vagueness and Belief}{February 21st}{APA Central Division Meeting}{Invited}{`Vagueness and Evidence'}
\cventry{2014}{M\&E Group Speaker Series at the University of Toronto}{November 13th}{University of Toronto}{Invited Talk}{`Relative Locations'}
\cventry{2014}{MIT Colloquium 2014}{September 26th}{Massachusetts Institute of Technology}{Invited Talk}{`Stalnaker's Thesis in Context'}
\cventry{2014}{Formal Epistemology Workshop 2014}{June 20-22}{University of Southern California}{Accepted Talk}{`Stalnaker's Thesis in Context'}
\cventry{2014}{Meaning and Modality}{June 2-4}{Center for the Study of Mind in Nature, University of Oslo}{Invited Talk}{`Vagueness, Possible Worlds and Precisifications'}
\cventry{2013}{BW8 Conditionals}{June 26-28}{University of Barcelona}{Accepted talk}{`In defence of a na\"{i}ve conditional epistemology'}
\cventry{2013}{UC Irvine Colloquium}{January 25}{University of California, Irvine}{Invited talk}{`In defence of a na\"{i}ve conditional epistemology'}
\cventry{2012}{The Philosophy of Mathematics Seminar}{May 1}{Oxford}{Invited talk}{`A general approach to revenge paradoxes'}
\cventry{2012}{Axiomatic vs. Semantic Truth}{March 14-16 }{Munich}{Accepted talk}{`A general approach to revenge paradoxes'}
\cventry{2011}{Mind, Language and Action}{August 29 - September 2}{Dubrovnik}{Invited speaker}{`A non-linguistic account of indeterminacy'}
\cventry{2010}{Workshop on Vagueness and Metaphysics, III}{September 16-17}{Barcelona}{Invited speaker}{`Vagueness at every order: the prospects of denying B'}
\cventry{2009}{Workshop on Truth and Probability}{September 22}{Bristol}{Invited speaker}{`Higher order indeterminacy and the revenge liar'}
\cventry{2009}{Ockham Society}{February 24}{Oxford}{}{`What to do when the world splits in two'}
\cventry{2008}{Ockham Society}{November}{Oxford}{}{`A really weird puzzle involving: a coin, a backwards supertask, and the axiom of choice'}
\cventry{2008}{Oxford/Paris Workshop on Language and Ontology}{June 26th--28th}{Paris}{Invited speaker}{`Representing Counterparts'}


\section{Teaching}

\subsection{Undergraduate teaching}

\cventry{PHIL 350}{Symbolic Logic}{Fall 2018, Spring 2020, Fall 2020, Spring 2022, Spring 2023, Spring 2024}{}{}{}
\cventry{PHIL 236}{Space and Time}{Fall 2018, Spring 2020, Spring 2023, Spring 2024}{}{}{}

\cventry{PHIL 450}{The Limits of Logic}{Spring 2018, Spring 2021}{}{}{}
\cventry{PHIL 120}{Introduction to Formal Logic}{Spring 2016, Fall 2016}{}{}{}
\cventry{ARLT 100}{Philosophical Paradoxes}{Spring 2013, Fall 2013}{}{}{}
\cventry{PHIL 460}{Metaphysics}{Fall 2013, Spring 2015}{}{}{}
\cventry{PHIL 465}{Philosophy of Language}{Spring 2022}{}{}{}
\cventry{PHIL 351}{Reasoning and Logic}{Fall 2014}{}{}{}

\cventry{PHIL 428}{Anglo-American Philosophy Since 1950}{Fall 2013}{}{}{}

\subsection{Graduate seminars}


%\cventry{PHIL 565}{Philosophy of Language}{Spring 2015}{}{}{}
\cventry{PHIL 570}{Seminar in Epistemology}{Spring 2014}{}{}{}
\cventry{PHIL 565}{Philosophy of Language}{Spring 2015, Fall 2015}{}{}{}
\cventry{PHIL 510}{Philosophical Logic}{Fall 2019, Fall 2020, Fall 2022}{}{}{}
\cventry{PHIL 551}{Philosophy of Logic}{Spring 2016, Fall 2016, Fall 2020}{}{}{}



\subsection{Supervision}

\cvitem{Undergraduate theses: Nathan Johnstone (with Gabriel Uzquiano), Qilin Ye (mathematics)}
\cvitem{First year mentorship}{Eliana Rabinowiz, Philip Li, Jin Zeng, Milana Kostic, Yudi Huang, Arthur Wu}
\cvitem{Qualifying exams}{Greg Ackerman, Keith Hall, Maegan Fairchild, Nathan Howard, Frank Hong, Zach Goodsell}
\cvitem{Area exams}{Maegan Fairchild, Jonathan Wright, Lee Killam, Douglas Wadle, Frank Hong, Brian Haas, Zach Goodsell, Kin Weng San, Yasha Sapir, Antonio Cleani, Milana Kostic, Jin Zeng}
\cvitem{Second year papers}{Zach Goodsell, Yasha Sapir, Antonio Cleani, Jin Zeng, Milana Kostic, Yudi Huang, Arthur Wu}
\cvitem{Dissertation committees}{Keith Hall, Jonathan Wright, Maegan Fairchild, Frank Hong (chair), Zach Goodsell (co-chair), Elif Uskuplu (mathematics, external member)}


\section{Service at USC}


\cvlistitem{Graduate placement: }
\cvlistitem{Hiring committee: 2013, 2014, 2016, 2017}
\cvlistitem{Graduate curriculum committee: 2013}
\cvlistitem{Graduate admissions:2014, 2015, 2018, 2021, 2022}
\cvlistitem{Graduate committee:2014, 2015, 2016}
\cvlistitem{Colloquium committee: 2014-2017 (chair), 2018-2023}
\cvlistitem{Peer teaching evaluation: 2022}
\cvlistitem{PPQ editorial committee: 2016, 2019}
\cvlistitem{Graduate recruitment: 2021}
\cvlistitem{Faculty review: 2019}
\cvlistitem{Third year review committee: 2019}
\cvlistitem{Helped draft statements for faculty going up for promotion: 2021}
\cvlistitem{Co-organized the 4th SoCal PhilMath, PhilLogic and FoM Workshop}
\cvlistitem{First year graduate student mentoring: Eliana Rabinowicz, Frank Hong, Philip Li, Jin Zeng}
\cvlistitem{Metaphysics subject co-editor, Pacific Philosophical Quarterly, 2016-2017}
\cvlistitem{Post-doc mentoring: Leif Hancox-Li}





(Dates refer to the start of the academic year of the service.)






\section{Other Professional activities}

\cvlistitem{Editor for the Review of Symbolic Logic (January 2018-21)}
\cvlistitem{Reviewer for Mind, Nous, The Journal of Philosophical Logic, Philosophers' Imprint, Philosophical Studies, Philosophia, The Notre Dame Journal of Formal Logic, Pacific Philosophical Quarterly, Res Philosophica, Review of Symbolic Logic, Analysis, Thought, Studia Logica, Topoi, Ratio, Inquiry, Synthese, Logique et Analyse and Erkenntnis. Reviewed books for: Oxford University Press}
%\cvlistitem{Juhani:Project partner}
%\cvlistitem{Jowett Society, committee member 2010-2011}
\cvlistitem{Formal Epistemology Workshop Programme Committee 2016 and 2018}


%\newpage 
%\section{Languages}
%\cvlanguage{language 1}{Skill level}{Comment}
%\cvlanguage{language 2}{Skill level}{Comment}
%\cvlanguage{language 3}{Skill level}{Comment}

%\section{Computer skills}
%\cvcomputer{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvcomputer{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvcomputer{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

%\section{Interests}
%\cvline{hobby 1}{\small Description}
%\cvline{hobby 2}{\small Description}
%\cvline{hobby 3}{\small Description}

\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.
